Equipo 7

### 2021-05-04 final/script.Rmd
pipe merge

#Ahora datos del 2010
censo_10<-read.csv("censo2010.csv")
planea_10<-read.csv("ENLACE_sec_2010.csv")

@@

#Preparacion
censo_10$ENTIDAD<-as.numeric(censo_10$ENTIDAD)
censo_10$MUN<-as.numeric(censo_10$MUN)
censo_10$LOC<-as.numeric(censo_10$LOC)

@@

#Preparacion
censo_10$ENTIDAD<-as.numeric(censo_10$ENTIDAD)
censo_10$MUN<-as.numeric(censo_10$MUN)
censo_10$LOC<-as.numeric(censo_10$LOC)

#Creo indice INEGI
censo_10<-censo_10%>%mutate(MUN=sprintf("%03d",censo_10$MUN),
                      ENT=sprintf("%02d",censo_10$ENTIDAD),
                      LOC=sprintf("%04d",censo_10$LOC)) %>% 
              mutate(a=paste(ENT,MUN,sep=""))%>% 
              mutate(INEGI=paste(a,LOC,sep=""))

>>>>

#Ahora datos del 2010
censo_10<-read.csv("http://ri.uaemex.mx/bitstream/handle/20.500.11799/58449/03%20Censo%20de%20poblaci%c3%b3n%20por%20localidades%202010.csv?sequence=2&isAllowed=y")
planea_10<-read.csv("ENLACE_sec_2010.csv")

@@

#Preparacion
censo$ENTIDAD<-as.numeric(censo$ENTIDAD)
censo$MUN<-as.numeric(censo$MUN)
censo$LOC<-as.numeric(censo$LOC)

@@

#Preparacion
censo_10$ClaveLoc<-as.numeric(censo_10$ClaveLoc)

#Creo indice INEGI
censo_10<-censo_10%>%mutate(INEGI=sprintf("%09d",censo_10$ClaveLoc))
